Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-28 paper/paper.tex
pass

In the following, we briefly show how \tname{} synthesizes rules for
this attack. The action and the header of the rules that \tname{}
creates are either inferred or left constant. For example, in this
case, \tname{} sets the action to \CodeIn{alert} and sets the header
to \CodeIn{<proto> any any -> any any}, indicating that it infers the
target protocol and uses the most general flow description possible,
\ie{}, it instructs the \nids\ to analyze the traffic flowing from/to
any address and port.  The rationale for this decision is that the
choice of these parameters are domain-specific and subject to change
by the system administrator.  The main challenge in synthesizing rules
is to discover the set of options in a rule that blocks the malicious
traffic, but allows the benign traffic to pass.

@@

Unfortunately, the relevant data for the option may be at the message
payload; not the fields. We found empirically that this occurs
frequently in http attacks, which are prevalent. For example,
\Fix{XXX\%} of the \numrulessuri{} rules from a public data
set~\cite{emerging-threats-open} we analyzed prescribe defenses
against http attacks. Figure~\ref{fig:rule-jboss} shows an example of
a rule that captures traffic containing the string
\CodeIn{"/HtmlAdaptor"} in the payload.  Content options are very
common in http rules---\percRulesWithContent{} of the rules from the
data set mentioned above contain at least one content
option. Figure~\ref{fig:distribution-contents} shows the histogram of
the number of these options per rule for the data set mentioned
above. We limited the number of content options per rule to 10 in the
histogram for space. \MyComment{Rules without \CodeIn{content} options
  are an exception and half of the rules contain at least two
  \CodeIn{content} options.}  Consequently, handling content options
for http is important. The content strategy focuses on extracting such
kinds of options from the payload.

@@

\subsubsection{Number of content options.} We empirically observed that content options are very
common. \Luc{Se for preciso temos numeros para fundamentar isso
  melhor, sao cerca de 70K contents nas 28K regras do
  data set}\Mar{sim, isto ajuda, porem mais importante eh saber quantas
  (\%) das 28K regras tem contents.} \Luc{sao 69417 contents nas 26094 regras q utilizam contents} As consequence, we defined a
heuristic function that takes the number of content options into
account. We calculate the contribution of number of content options
with the following formula:

@@

\begin{figure*}[t!]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{  
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,2134) (1,9164) (2,5103) (3,5841) (4,1987) (5,1622) (6,805) (7, 535) (8, 340) (9,154) (10, 53)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-1ex}
  \caption{\label{fig:distribution-contents}Number of content options.}
\end{subfigure}% <---- don't forget this %
%\vspace{1ex}
%\\
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,11) (1,1301) (2,4910) (3,3662) (4,3250) (5,5353) (6,2911) (7, 1337) (8, 1246) (9,763) (10, 495)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-1ex}
  \caption{\label{fig:distribution-rule-size}Rule sizes.}
\end{subfigure}%
%\vspace{1ex}
\\
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{  
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={GET, POST, SELECT, UNION, id=, DELETE, UPDATE, INSERT, 200, /index.php?},
          xtick=data,
          xticklabel style={rotate=45},          
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(GET,2007) (POST,1570) (SELECT,747) (UNION,461) (id=,408) (DELETE,390) (UPDATE,387) (INSERT, 386) (200, 352) (/index.php?, 273)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-3ex}  
  \caption{\label{fig:distribution-strings}Strings used as parameters of content options.}
\end{subfigure}%
%\vspace{1ex}
%\\
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{
    \begin{tikzpicture}
      \begin{axis}[
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          %          ylabel={\#rules},
          symbolic x coords={http\_method, http\_uri, http\_user\_agent, http\_header, http\_host, http\_connection, http\_request\_line},
          xtick=data,
          xticklabel style={rotate=45},          
          nodes near coords,
          every node near coord/.append style={font=\scriptsize},        
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(http\_method,3821) (http\_uri,10111) (http\_user\_agent,1022) (http\_header,4089) (http\_host,224) (http\_connection,29) (http\_request\_line,11)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-1ex}
  \caption{\label{fig:distribution-content_modifiers}Content modifiers
    frequency.}
\end{subfigure}%
\vspace{-1ex}
  \caption{Distribution of features.}
  \Luc{@Marcelo, estamos utilizando mais uma distribuicao agora. Precisamos adicionar o grafico dela tb?}
\end{figure*}

@@

    JBoss JMX\MyComment{ Console Beanshell Exploit} & Nikto2 & RCE & HTTP \MyComment{& Remote Code Execution} & \textbf{content}:"/HtmlAdaptor"; nocase; http\_uri; \textbf{content}:"action=inspect"; nocase; http\_uri; \textbf{content}:"bean"; nocase; http\_uri; \textbf{content}:"name="; http\_uri; \\
    %% WeBid \MyComment{Local File Inclusion} & RFI & TCP \MyComment{& Local File Inclusion} & \textbf{content}:"GET "; depth:4; \textbf{content}:"/cron.php?"; http\_uri; nocase; \textbf{content}:"include\_path="; http\_uri; nocase; \textbf{content}:"../"; \\
    ColdFusion \MyComment{PESC} & Nikto2 & PESC & HTTP \MyComment{& Privilege Escalation} & \textbf{content}:"GET"; http\_method; nocase; \textbf{content}:"/CFIDE/administrator"; http\_uri; nocase; \\
    .htaccess access\MyComment{attempted-recon} & Nikto2 & AREC & HTTP \MyComment{& Adicionar} & \textbf{content}:".htaccess"; nocase; http\_uri; \\
    .idq access\MyComment{EXPLOIT ISAPI} & Nikto2 & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:".idq"; nocase; http\_uri; \\
    iisadmin access\MyComment{web-application-attack} & Nikto2 & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"/iisadmin"; nocase; http\_uri; \\
    /system32/ in URI\MyComment{Possible Protected Directory Access Attempt} & Nikto2 & AREC & HTTP \MyComment{& Adicionar} & \textbf{content}:"/system32/"; nocase; http\_uri; \\
    Script tag in URI\MyComment{Possible Cross Site Scripting Attempt} & Nikto2 & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"</script>"; nocase; http\_uri; \\
    \bottomrule
  \end{tabular}
\end{table*}

@@

    \midrule
    Ping Scan & 5 & 5 & 2 & - \\
    SYN Flood & 3 & 2 & 2 & - \\
    JBoss JMX & 4 & 23 & 381 & 23 \\
    %%   WeBid & - & 23 & - & -\\    
    ColdFusion & 6 & 19 & 39 & 5\\
    .htaccess access & 4 & 17 & 2,458 & 2\\
    .idq access & 13 & 19 & 1,111 & 2 \\
    iisadmin access & 3 & 17 & 861 & 1 \\
    /system32/ in URI & 3 & 20 & 3,665 & 2 \\
    Script tag in URI & 22 & 22 & - & - \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\vspace{1ex}
\subsubsection{Attacks.}~Table~\ref{table:attacks} shows the selection
of attacks considered in our evaluation.  Column ``Name'' shows the
name of the attack, column ``Source'' shows the source where we
obtained data to reproduce the attack (see
Section~\ref{subsec:malicious-traffic}), column ``Type'' shows the
kind of attack, column ``Protocol'' shows the name of the protocol
explored in the attack, and column ``Ground Truth'' shows the rule
options to capture the attack. The rationale for the selection were
(1) to cover attacks with different characteristics, (2) to cover
attacks of various protocols, and (3) to explore different features of
\tname. As for (1), the selection includes attacks of the following
types: Denial-of-Service (DoS), Active Reconnaissance (AREC),
Privilege escalation (PESC), and Remote Code Execution (RCE). Note
that the distribution of attacks is not uniform across protocols as
these distributions are not uniform in practice---http attacks are
prevalent.

@@

\subsubsection{\label{subsec:malicious-traffic}Malicious traffic.}~Recall that \tname\ takes
pcap files on input. As explained on Section~\ref{sec:minimization},
these files abstract network messages~\cite{pcap} and can be used to
avoid network traffic during rule synthesis. For some of the attacks
listed on Table~\ref{table:attacks}, we obtained pcap files directly
from trusted security websites (\eg{},
NetReseC~\cite{pcap-attacks}\Fix{confirm}).\Mar{reminder: we still
  don't have any example of attack listed on Table~\ref{table:attacks}
  whose pcap file was obtained from those websites.} In addition to
these sources, we used the Nikto2~\cite{nikto} open source security
tool as follows to obtain pcap files for (non-flooding) http and tcp
attacks. We configured an http server (Apache2) and ran Nikto2 to
attack that server. Simultenously, we ran
WireShark~\cite{wireshark-net-monitor} to record the network traffic
and Suricata to analyze the traffic. We configured \suri\ with all
rules from the ``Emerging Threats Open
Ruleset''~\cite{emerging-threats-open} and configured Nikto2 with
default parameters, which makes it replay all recorded attacks. After
execution, we inspected the \suri\ log to identify which rules have
been activated and which packets were involved on each
activation. With the packet numbers, it is possible to recover the
corresponding pcap files, using Wireshark, as to ran \tname{} on
them. It is worth noting that some rules are triggered multiple times,
indicating that Nikto2 expresses multiple variants of the same
attack. RQ3 evaluates the importance of these variants to \tname{}'s
performance. We used similar methodology to obtain pcap files using
other security testing tools. We used NMAP~\cite{netmap} to reproduce
the Ping Scan attack (see Section~\ref{sec:active-recon}) and
hping3~\cite{hping3} to reproduce the SYN Flood attack (see
Section~\ref{sec:dos}).

>>>>

In the following, we briefly show how \tname{} synthesizes rules for
this attack. The action and the header of the rules that \tname{}
creates are either inferred or left constant. For example, in this
case, \tname{} sets the action to \CodeIn{alert} and sets the header
to \CodeIn{<proto> any any -> any any}, indicating that it infers the
target protocol and uses the most general flow description possible,
\ie{}, it instructs the \nids\ to analyze the traffic flowing from/to
any address and port.  The rationale for this decision is that the
choice of these parameters are domain-specific and subject to change
by the system administrator.  The main challenge in synthesizing rules
is to discover the set of options in a rule that blocks the malicious
traffic, but allows the benign traffic to pass. \Luc{O Suricata normalmente 
nao bloqueia trafego, apenas gera alertas sobre ele. Para bloquear um 
pacote ele precisa ser configurado no modo Intrusion Prevention System 
(IPS) ao inves de IDS: https://blog.starti.com.br/ids-ips/}

@@

Unfortunately, the relevant data for the option may be at the message
payload; not the fields. We found empirically that this occurs
frequently in http attacks, which are prevalent. For example,
\Fix{\Luc{53\%}} of the \numrulessuri{} rules from a public data
set~\cite{emerging-threats-open} we analyzed prescribe defenses
against http attacks. Figure~\ref{fig:rule-jboss} shows an example of
a rule that captures traffic containing the string
\CodeIn{"/HtmlAdaptor"} in the payload.  Content options are very
common in http rules---\percRulesWithContent{} of the rules from the
data set mentioned above contain at least one content
option. Figure~\ref{fig:distribution-contents} shows the histogram of
the number of these options per rule for the data set mentioned
above. We limited the number of content options per rule to 10 in the
histogram for space. \MyComment{Rules without \CodeIn{content} options
  are an exception and half of the rules contain at least two
  \CodeIn{content} options.}  Consequently, handling content options
for http is important. The content strategy focuses on extracting such
kinds of options from the payload.

@@

\subsubsection{Number of content options.} We empirically observed that content options are very
common. \Luc{Se for preciso temos numeros para fundamentar isso
  melhor, sao cerca de 70K contents nas 28K regras do
  data set}\Mar{sim, isto ajuda, porem mais importante eh saber quantas
  (\%) das 28K regras tem contents.} \Luc{92\%} As consequence, we defined a
heuristic function that takes the number of content options into
account. We calculate the contribution of number of content options
with the following formula:

@@

\begin{figure*}[t!]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{  
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,2134) (1,9164) (2,5103) (3,5841) (4,1987) (5,1622) (6,805) (7, 535) (8, 340) (9,154) (10, 53)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-1ex}
  \caption{\label{fig:distribution-contents}Number of content options.}
\end{subfigure}% <---- don't forget this %
%\vspace{1ex}
%\\
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,11) (1,1301) (2,4910) (3,3662) (4,3250) (5,5353) (6,2911) (7, 1337) (8, 1246) (9,763) (10, 495)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-1ex}
  \caption{\label{fig:distribution-rule-size}Rule sizes.}
\end{subfigure}%
%\vspace{1ex}
\\
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{  
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={GET, POST, SELECT, UNION, id=, DELETE, UPDATE, INSERT, 200, /index.php?},
          xtick=data,
          xticklabel style={rotate=45},          
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(GET,2007) (POST,1570) (SELECT,747) (UNION,461) (id=,408) (DELETE,390) (UPDATE,387) (INSERT, 386) (200, 352) (/index.php?, 273)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-3ex}  
  \caption{\label{fig:distribution-strings}Strings used as parameters of content options.}
\end{subfigure}%
%\vspace{1ex}
%\\
\begin{subfigure}{.5\textwidth}
  \centering
  \scalebox{1.2}{
    \begin{tikzpicture}
      \begin{axis}[
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          %          ylabel={\#rules},
          symbolic x coords={http\_method, http\_uri, http\_user\_agent, http\_header, http\_host, http\_connection, http\_request\_line},
          xtick=data,
          xticklabel style={rotate=45},          
          nodes near coords,
          every node near coord/.append style={font=\scriptsize},        
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(http\_method,3821) (http\_uri,10111) (http\_user\_agent,1022) (http\_header,4089) (http\_host,224) (http\_connection,29) (http\_request\_line,11)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-1ex}
  \caption{\label{fig:distribution-content_modifiers}Content modifiers
    frequency.}
\end{subfigure}%
\vspace{-1ex}
  \caption{Distribution of features.}
\end{figure*}

@@

    JBoss JMX\MyComment{ Console Beanshell Exploit} & Nikto2 & RCE & HTTP \MyComment{& Remote Code Execution} & \textbf{content}:"/HtmlAdaptor"; nocase; http\_uri; \textbf{content}:"action=inspect"; nocase; http\_uri; \textbf{content}:"bean"; nocase; http\_uri; \textbf{content}:"name="; http\_uri; \\
    WeBid \MyComment{Local File Inclusion} & RFI & HTTP & \Fix{LFI} & \textbf{content}:"GET "; depth:4; \textbf{content}:"/cron.php?"; http\_uri; nocase; \textbf{content}:"include\_path="; http\_uri; nocase; \textbf{content}:"../"; \\
    ColdFusion \MyComment{PESC} & Nikto2 & PESC & HTTP \MyComment{& Privilege Escalation} & \textbf{content}:"GET"; http\_method; nocase; \textbf{content}:"/CFIDE/administrator"; http\_uri; nocase; \\
    .htaccess access\MyComment{attempted-recon} & Nikto2 & AREC & HTTP \MyComment{& Adicionar} & \textbf{content}:".htaccess"; nocase; http\_uri; \\
    .idq access\MyComment{EXPLOIT ISAPI} & Nikto2 & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:".idq"; nocase; http\_uri; \\
    iisadmin access\MyComment{web-application-attack} & Nikto2 & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"/iisadmin"; nocase; http\_uri; \\
    /system32/ in URI\MyComment{Possible Protected Directory Access Attempt} & Nikto2 & AREC & HTTP \MyComment{& Adicionar} & \textbf{content}:"/system32/"; nocase; http\_uri; \\
    Script tag in URI\MyComment{Possible Cross Site Scripting Attempt} & Nikto2 & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"</script>"; nocase; http\_uri; \\
    Apache Struts 2 & \Fix{Source} & \Fix{RCE} & HTTP & \textbf{content}:"POST"; http\_method; \textbf{content}:"java.lang.ProcessBuilder"; nocase; http\_client\_body; fast\_pattern; \textbf{content}:"/struts2-rest-showcase/orders/3"; http\_uri; \\
    WordPress Login & \Fix{Source} & Policy Violation & HTTP & \textbf{content}:"log="; http\_client\_body; \textbf{content}:"\&pwd="; http\_client\_body; \textbf{content}:"\&wp-submit="; http\_client\_body; \\
    \bottomrule
  \end{tabular}
\end{table*}

@@

    \midrule
    Ping Scan & 5 & 5 & 2 & - \\
    SYN Flood & 3 & 2 & 2 & - \\
    JBoss JMX & 4 & 23 & 228 & \Fix{23} \\
    WeBid & 1 & 23 & - & -\\    
    ColdFusion & 6 & 19 & 34 & \Fix{5}\\
    .htaccess access & 4 & 17 & 984 & \Fix{2}\\
    .idq access & 13 & 19 & 511 & \Fix{2} \\
    iisadmin access & 3 & 17 & \Fix{861} & \Fix{1} \\
    /system32/ in URI & 3 & 20 & 1,913 & \Fix{2} \\
    Script tag in URI & 22 & 22 & 786 & - \\
    Apache Struts 2 & - & - & - & - \\
    Wordpress Login & - & - & - & - \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\vspace{1ex}
\subsubsection{Attacks.}~Table~\ref{table:attacks} shows the selection
of attacks considered in our evaluation.  Column ``Name'' shows the
name of the attack, column ``Source'' shows the source where we
obtained data to reproduce the attack (see
Section~\ref{subsec:malicious-traffic}), column ``Type'' shows the
kind of attack, column ``Protocol'' shows the name of the protocol
explored in the attack, and column ``Ground Truth'' shows the rule
options to capture the attack. The rationale for the selection were
(1) to cover attacks with different characteristics, (2) to cover
attacks of various protocols, and (3) to explore different features of
\tname. As for (1), the selection includes attacks of the following
types: Denial-of-Service (DoS), Active Reconnaissance (AREC),
Privilege escalation (PESC), Remote Code Execution (RCE), \Luc{Local 
File Inclusion (LFI) and Policy Violation (PV)}. Note that the 
distribution of attacks is not uniform across protocols as these 
distributions are not uniform in practice---http attacks are prevalent.

@@

\subsubsection{\label{subsec:malicious-traffic}Malicious traffic.}~Recall that \tname\ takes
pcap files on input. As explained on Section~\ref{sec:minimization},
these files abstract network messages~\cite{pcap} and can be used to
avoid network traffic during rule synthesis. For some of the attacks
listed on Table~\ref{table:attacks}, we obtained pcap files directly
from trusted security websites (\eg{},
NetReseC~\cite{pcap-attacks}\Fix{confirm}).\Mar{reminder: we still
  don't have any example of attack listed on Table~\ref{table:attacks}
  whose pcap file was obtained from those websites.} \Luc{Ataques Apache 
  e WordPress. @Guilherme adicionar fontes} In addition to
these sources, we used the Nikto2~\cite{nikto} open source security
tool as follows to obtain pcap files for (non-flooding) http and tcp
attacks. We configured an http server (Apache2) and ran Nikto2 to
attack that server. Simultenously, we ran
WireShark~\cite{wireshark-net-monitor} to record the network traffic
and Suricata to analyze the traffic. We configured \suri\ with all
rules from the ``Emerging Threats Open
Ruleset''~\cite{emerging-threats-open} and configured Nikto2 with
default parameters, which makes it replay all recorded attacks. After
execution, we inspected the \suri\ log to identify which rules have
been activated and which packets were involved on each
activation. With the packet numbers, it is possible to recover the
corresponding pcap files, using Wireshark, as to ran \tname{} on
them. It is worth noting that some rules are triggered multiple times,
indicating that Nikto2 expresses multiple variants of the same
attack. RQ3 evaluates the importance of these variants to \tname{}'s
performance. We used similar methodology to obtain pcap files using
other security testing tools. We used NMAP~\cite{netmap} to reproduce
the Ping Scan attack (see Section~\ref{sec:active-recon}) and
hping3~\cite{hping3} to reproduce the SYN Flood attack (see
Section~\ref{sec:dos}).
